Procedural generation of levels for the angry birds videogame using evolutionary computation\\

### 2019-05-15 IEEE_ConferenceOnGames/new_article.tex
Removed blank cite
Error on abstract

\begin{abstract}
    % We do not say this project, is more like: In this paoer an evolutionary ... 
    % is presented or In this paper we present a .... (in third or first person plural) - MG   
    In this paper an evolutionary computation-based system is proposed to generate 
    levels for the Angry Birds video game, the levels themselves are composed of a 
    set of birds that the player can use, a certain amount of pigs that must be destroyed 
    in order to progress to the next level and a given number of pieces that conform 
    structures that may or may not protect the pigs from the player. The focus in this stage
    is the generation of diverse structures that can be played in the game having the
    additional characteristics of being interesting and playable. We propose a 
    multi-layered search, first contructing composite structures from basic components, to then
    build more complex structures building from these components, following an open-ended 
    evolution approach; in which the evolution of structures is not guided towards 
    a single objective but rather is free to evolve and generate novelty or diversity. 
    The objective is then that the proposed levels are evaluated by how complex they become and how 
    different they are from the rest of the group. The experiments conducted show that a evolutionary approach allows the generated levels
    to have a level of uniqueness because on most of the cases the way they are presented on screen
    is a way a normal human would have trouble to create but at the same time are interesting to see.
    % Maybe like this ? JSH
    %The experiments conducted show  
    % We found that in the experiments conducted, levels generated where ...

@@

    Structures are the next evolutionary layer, at a higher level of composition.
    Structures are compositions of composites. A level can be seen as a collection 
    of structures and each structure is a pile of composite blocks. This approach 
    was proposed by \cite{ }. This way of constructing levels has the advantage of
    limiting the search space, to structures that have a better chance to be 
    standing after the simulation ends. There is no warranty that piles of 
    composite blocks will maintain balance, so again we must search for those 
    structures.

>>>>

\begin{abstract}
    % We do not say this project, is more like: In this paoer an evolutionary ... 
    % is presented or In this paper we present a .... (in third or first person plural) - MG   
    In this paper an evolutionary computation-based system is proposed to generate 
    levels for the Angry Birds video game, the levels themselves are composed of a 
    set of birds that the player can use, a certain amount of pigs that must be destroyed 
    in order to progress to the next level and a given number of pieces that conform 
    structures that may or may not protect the pigs from the player. The focus in this stage
    is the generation of diverse structures that can be played in the game having the
    additional characteristics of being interesting and playable. We propose a 
    multi-layered search, first constructing composite structures from basic components, to then
    build more complex structures building from these components, following an open-ended 
    evolution approach; in which the evolution of structures is not guided towards 
    a single objective but rather is free to evolve and generate novelty or diversity. 
    The objective is then that the proposed levels are evaluated by how complex they become and how 
    different they are from the rest of the group. The experiments conducted show that a evolutionary approach allows the generated levels
    to have a level of uniqueness because on most of the cases the way they are presented on screen
    is a way a normal human would have trouble to create but at the same time are interesting to see.
    % Maybe like this ? JSH
    %The experiments conducted show  
    % We found that in the experiments conducted, levels generated where ...

@@

    Structures are the next evolutionary layer, at a higher level of composition.
    Structures are compositions of composites. A level can be seen as a collection 
    of structures and each structure is a pile of composite blocks. This way of 
    constructing levels has the advantage of
    limiting the search space, to structures that have a better chance to be 
    standing after the simulation ends. There is no warranty that piles of 
    composite blocks will maintain balance, so again we must search for those 
    structures.
